The Globular Cluster System of the Auriga Simulations

### 2019-03-26 AurigaGCS.tex
Implemented v0.01 of Sec. 4.2, now moving on

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma}.png}
    \caption{
        Mean and standard deviation of the metallicity distribution of star
        particles in our Auriga subsets compared to the MW (M31) GCS shown in
        purple (magenta). The black solid (open) dot shows values of the
        metal-rich (metal-poor) component of the MW GCS as quoted by
        \citep[][p. 38]{1998gcs..book.....A}.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

Figure~\ref{fig:FeH_mu_sigma} shows the mean and standard deviation of the
[Fe/H] distribution of star particles in the Auriga simulations. The mean
metallicity of old star particles lies in the range $-1.0$ to $-0.5$ and the
dispersion increases with decreasing metallicity. For comparison, the mean
of all star particles populates the range $-0.25$ to $0$ with a near-constant
dispersion a bit above $0.5$. Old accreted stars in the Auriga haloes reach
mean metallicities between $-1.5$ and $-1.0$, which is considerably lower than
the old- and old insitu populations. Most Auriga L4 haloes have old insitu
populations with mean metallicities around $-0.5$. The old accreted populations
follow the trent of increasing dispersion with decreasing mean metallicity, but
notably the old insitu populations all have a constant dispersion of roughly
$0.45$. We show the values calculated using all MW (M31) GCs in purple (magenta),
and literature values of the metal-rich (metal-poor) component of the MW GCS
as black solid (open) dots. We further discuss the comparison between the
simulations and the observations in Sec.~\ref{sec:discussion_FeH}

Figure~\ref{fig:FeH} shows the mass-weighted metallicity distribution of the
Auriga L4 haloes. Lines show the median value and the shaded regions indicate
the $1\sigma$ interval around it (i.e. scatter between runs with different initial
conditions which thus have unique merger histories). We notice again that
the peak metallicity shifts down from $0$ to $-0.5$ for old stars (orange solid)
compared to all stars (orange dotted) while the mass at the peak lowers by 
roughly one dex. The mass budget of the old stars is
dominated by the old insitu population (blue solid) below [Fe/H]=$-1$, and by
the old accreted stars (red solid) above this value. We show the MW (M31) GCS 
in purple (magenta) and we show the ratio of the simulated to the observed 
profiles in the middle (bottom) panel. This mass excess can be thought of as a
combination of the bound cluster formation efficiency and disruptive processes,
further discussed in Sec.~\ref{sec:discussion_mass_excess}.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (orange dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; orange solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}

% We notice a scatter\footnote{Here scatter means the width of the 1$\sigma$ interval.
% The difference between the minimum and maximum values is $0.9$~dex.} in mass
% normalization of $0.3$ dex between the different Auriga galaxies. We investigate
% whether there is a correlation between the total stellar mass in (old) star particles
% and the virial mass\footnote{The virial mass is defined as the mass contained
% inside the radius $r_{200,c}$ at which the average (spherical) mass density
% equals two hundred times the critical density of the Universe} $M_{200,c}$ of
% the host halo. We fit $a \cdot \left(\text{M}_{200,c}[1\text{e}10 \text{M\Sun}]
% - 140\right) + b$ to log$_{10}\left(\Sigma_{i} m_i(\text{\scriptsize [Fe/H] =
% -3})\right)$. % \limits_{i, \text{if age(i) $>$ 10~Gyr}}
% Our fit thus provides the slope $a$ and normalization of (old) stellar mass $b$
% at [Fe/H]=-3 for $M_{200,c}$ at 140e10~M\Sun. We find $a = 0.00388$, $b = 6.597$
% and conclude that there is a small positive correlation of mass in (old) star
% particles with the virial mass of the host halo.
%
% \begin{figure}
% \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit3}.png}
%     \caption{
%         Plot of log$_{10}$(mass normalization) [i.e. $b$ obtained above] against
%         the virial mass M$_{200,c}$ of the Auriga haloes. We fit a linear relation
%         to see whether there is a correlation, and find $a = 0.00388$, $b = 6.597$.
%         % Colours indicate resolution: L3 green, L4 orange, and L5 blue.
%         The red dotted line shows the `central' value of M$_{200,c}$, the yellow
%         region shows the 1$\sigma$ interval around the best-fit relation, and the
%         blue dashed lines shows the intrinsic scatter. The error bars show 1\%
%         of the obtained values.
%         \label{fig:Mnorm-fit}
%     }
% \end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{Rgc_mu_sigma}.png}
    \caption{
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (orange dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; orange solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}

@@

\subsection{Total mass in metallicity-radial space}
\label{sec:results_FeHRgc}
\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_36bins_mean-trim}.png}
    \caption{
        Ratio
        \label{fig:Au-FeHRgc-ratio}
    }
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma}.png}
    \caption{
        Mean and standard deviation of the metallicity distribution of star
        particles in each of the thirty Auriga L4 haloes. Orange dots show 
        the subset of old star particles, and blue (red) dots show the old 
        insitu (accreted) component. These Auriga subsets can be compared to 
        the MW (M31) GCS shown in purple (magenta), and to the metal-rich 
        (metal-poor) component of the MW GCS indicated by the black solid (open) 
        dots \citep[values from][p. 38]{1998gcs..book.....A}.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}
Figure~\ref{fig:FeH_mu_sigma} shows the mean and standard deviation of the
[Fe/H] distribution of star particles in all Auriga L4 simulations. The mean
metallicity of old star particles lies in the range $-1.0$ to $-0.5$ and the
dispersion increases with decreasing metallicity. For comparison, the mean
of all star particles populates the range $-0.25$ to $0$ with a near-constant
dispersion a bit above $0.5$. Old accreted stars in the Auriga haloes reach
mean metallicities between $-1.5$ and $-1.0$, which is considerably lower than
the old- and old insitu populations. Most Auriga L4 haloes have old insitu
populations with mean metallicities around $-0.5$. The old accreted populations
follow the trent of increasing dispersion with decreasing mean metallicity, but
notably the old insitu populations all have a constant dispersion of roughly
$0.45$. We show the values calculated using all MW (M31) GCs in purple (magenta),
and literature values of the metal-rich (metal-poor) component of the MW GCS
as black solid (open) dots. We further discuss our comparison between the
simulations and the observations in Sec.~\ref{sec:discussion_FeH}

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (orange dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; orange solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
Figure~\ref{fig:FeH} shows the mass-weighted metallicity distribution of the
Auriga L4 haloes. Lines show the median value and the shaded regions indicate
the $1\sigma$ interval around it (i.e. scatter between runs with different initial
conditions which thus have unique merger histories). We notice again that
the peak metallicity shifts down from $0$ to $-0.5$ for old stars (orange solid)
compared to all stars (orange dotted) while the mass at the peak lowers by 
roughly one dex. The mass budget of the old stars is
dominated by the old insitu population (blue solid) below [Fe/H]=$-1$, and by
the old accreted stars (red solid) above this value. We show the MW (M31) GCS 
in purple (magenta) and we show the ratio of the simulated to the observed 
profiles in the middle (bottom) panel. This mass excess can be thought of as a
combination of the bound cluster formation efficiency and disruptive processes,
further discussed in Sec.~\ref{sec:discussion_mass_excess}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{Rgc_mu_sigma}.png}
    \caption{
        Mean and standard deviation of the radial distribution of star particles
        in each of the thirty Auriga L4 haloes compared to the MW (M31) GCS 
        shown in purple (magenta).
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
Figure~\ref{fig:Rgc_mu_sigma} shows the mean and standard deviation of the
radial distribution of star particles in all Auriga L4 simulations. We notice 
that the old insitu populations are much more centrally distributed, whereas
the old accreted component has a larger radial extent. Moreover, the dispersion
increases with increasing mean value of the radial distribution.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (orange dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; orange solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}
Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
particles that is not present for the old star particles, indicating that the
stellar disc is no longer present when applying the latter selection criterion.
Furtermore, we find that the dominant contribution to the total mass in old
stars changes from those formed insitu to the accreted population around 
$10$~kpc. We further discuss our comparison between the simulations and the 
observations in Sec.~\ref{sec:discussion_Rgc}.

@@

\subsection{Total mass in metallicity-radial space}
We investigate whether the Auriga simulations still produce sufficient mass in 
old star particles to be consistent with the MW (M31) GCS when two-dimensionally 
binned in both [Fe/H] and $R_\text{GC}$. We sum the total simulated mass in 
each bin and then divide it by the total mass in the MW (M31) GCS. We show this
mass excess in Figure~\ref{}, respectively Figure~\ref{}
\label{sec:results_FeHRgc}
\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_36bins_mean-trim}.png}
    \caption{
        Ratio
        \label{fig:Au-FeHRgc-ratio}
    }
\end{figure}
